Unveiling Robustness Threats by Mining the Exception Stack Traces of over 600 Android Projects

### 2014-09-05 android-stacks.tex
activity

To investigate the obedience to such practice, we firstly filtered out all the exceptions implicitly
 signaled by  runtime environment (due to programming mistakes) since these exceptions 
should not be documented on the method signature. Then we inspected the code each method 
(defined either on Android or on libraries) signaling  runtime exceptions not-related to programming mistakes.
As a result of this inspection, we could observe that only 1 method out of 118 inspected methods
 (i.e., 0,8\%) documented the explicitly thrown runtime exception in a Javadoc comment; and none of these methods
included the runtime exception  (reported on the stack) as part of the exception interface of the method (i.e., using 
throws clause on method signature). This result is aligned with the results of other study conducted by from 
Sacramento et al ~\cite{sacramento2006unchecked} which observed that the
runtime exceptions in .Net programs are most often not documented.

@@

%SELECT repo, *
% FROM stacktracesummary where stack like '%getDeclaredMethods%';

@@

>>>>

To investigate the obedience to such practice, we firstly filtered out all the exceptions implicitly
 signaled by  runtime environment (due to programming mistakes) since these exceptions 
should not be documented on the method signature.

Then we inspected the code each method (defined either on Android  Aplication Framework or on libraries) 
explicitly signaling a runtime exception not-related to programming mistakes.
As a result of this inspection, we could observe that only 1 method out of 118 inspected methods
 (i.e., 0,8\%) documented the explicitly thrown runtime exception in a Javadoc comment; and none of these methods
included the runtime exception  (reported on the stack) as part of the exception interface of the method (i.e., using 
throws clause on method signature). This result is aligned with the results of other study conducted by from 
Sacramento et al ~\cite{sacramento2006unchecked} which observed that the
runtime exceptions in .Net programs are most often not documented.

@@

@@

During the manual inspection, besides inspecting the code of exception signalers we also
inspected the intermediate methods reported on the stacks.  The inspected stack traces envolved, 
in one way or another, methods from the  Android Application Framework: either framework 
utility methods, or framework hook methods  (e.g., OnCreate(), onPause()).
During this inspection we could observe that none of the hook methods provided by the Activity class 
specify an exception interface.  The``exception interface" can stimulate
can stimulate the developer (in this case, extending Activity class) to: think that 
``something" may go wrong during the execution of such methods; and design the 
exception handling code accordingly (the absence of such interface
 violates to best practice IV).

\noindent \fbox{ \begin{minipage}{0.96\columnwidth} \emph{
 None of the Activity hook methods define an ``exception interface".
}
\end{minipage}}
